### 2017-01-03 paper/paris17/paper.tex
fix citation

The concept of the constant-Q model introduced by \cite{Kjartansson.sep.23} is used to approximate the attenuation. However, the formulation for computing the time derivative of the constant-Q model requires to store wavefields from previous values to present time \cite[]{podlubny1998fractional}, which is impractical for real seismic modeling in terms of memory capacities on modern computers. Zhu developed a constant-Q wave equation using fractional Laplacian operators which avoid the need for storing the past values of the wavefields \cite[]{zhu2014theory}. However, the proposed method is for the 2D viscoelastic case and the computational cost of fractional Laplacian is still expensive compared with the conventional Laplacian.

>>>>

The concept of the constant-Q model introduced by \cite{Kjartansson.sep.23} is used to approximate the attenuation. However, the formulation for computing the time derivative of the constant-Q model requires to store wavefields from previous values to present time, which is impractical for real seismic modeling in terms of memory capacities on modern computers. Zhu developed a constant-Q wave equation using fractional Laplacian operators which avoid the need for storing the past values of the wavefields \cite[]{zhu2014theory,shen2013wave,shen2015image}. However, the proposed method is for the 2D viscoelastic case and the computational cost of fractional Laplacian is still expensive compared with the conventional Laplacian.
